Alberta's Electricity Market

### 2022-01-27 paper/paper_draft.tex
fixing graphs

\begin{figure}[t]%%
	\centering \vspace{-.25cm} \includegraphics[width=6.5in]{../../SGER/sector_compliance_cost.png}
\vspace{-0.75cm}	\caption{Upper: Generation-weighted annual average compliance cost (black lines) and individual plant realizations (lighter grey lines) by plant type. Lower: Price charged on excess net annual emissions under Alberta's carbon pricing programs. Source: Alberta Environment compliance cost data.}
\label{fig:sector_compliance_cost}
\end{figure}

>>>>

\begin{figure}[t]%%
	\centering \vspace{-.25cm} \includegraphics[width=6.5in]{../../SGER/sector_compliance_cost.png}
\vspace{-0.75cm}	\caption{Generation-weighted annual average compliance cost (dashed black lines) and individual plant realizations (lighter grey lines) by plant type (\$/MWh), combined with the price charged on excess net annual emissions (black lines) under Alberta's carbon pricing programs (\$/tonne). Coal plants and natural gas combined-cycle (NGCC) and simple-cycle (SCGT) plants with more than 20MW installed capacity are shown. Source: Alberta Environment compliance cost data combined with AESO generation data provided by NRGStream.}
\label{fig:sector_compliance_cost}
\end{figure}
